---
title: "Awesome ggplot2 Resources"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(jsonlite)
library(dplyr)
library(reactable)
library(htmltools)
library(stringr)

# Read JSON data
json_data <- fromJSON("readme_data.json", simplifyVector = FALSE)

# Helper function to flatten the JSON structure into a dataframe
flatten_json <- function(json_data) {
  rows <- list()
  
  for (section_name in names(json_data)) {
    section <- json_data[[section_name]]
    
    if (is.list(section)) {
      for (subsection_name in names(section)) {
        subsection <- section[[subsection_name]]
        
        if (is.list(subsection)) {
          for (item in subsection) {
            if (!is.null(item$name)) {
              rows[[length(rows) + 1]] <- list(
                section = section_name,
                subsection = subsection_name,
                name = item$name,
                url = item$url,
                description = item$description
              )
            }
          }
        }
      }
    }
  }
  
  df <- do.call(rbind.data.frame, rows)
  return(df)
}

# Convert JSON to dataframe
resources_df <- flatten_json(json_data)
```

Column {.sidebar}
=====================================

### About

This dashboard provides an interactive way to explore awesome ggplot2 resources. Use the built-in table filters and search functionality to find resources. Click on resource names to visit their websites.

Features:

- Filter by any column
- Full-text search across all fields
- Sortable columns
- Direct links to resources
- Responsive layout

Statistics:
- Total Resources: `r nrow(resources_df)`
- Categories: `r length(unique(resources_df$section))`

Main Content
=====================================

### ggplot2 Resources {.no-padding}

```{r}
reactable(
  resources_df,
  filterable = TRUE,
  searchable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  compact = TRUE,
  defaultPageSize = 20,
  defaultSorted = list(section = "asc"),
  columns = list(
    section = colDef(
      name = "Section",
      minWidth = 150,
      filterInput = function(values) {
        tags$select(
          tags$option(value = "", "All"),
          lapply(unique(values), function(value) {
            tags$option(value = value, value)
          })
        )
      }
    ),
    subsection = colDef(
      name = "Subsection",
      minWidth = 150
    ),
    name = colDef(
      name = "Name",
      minWidth = 200,
      cell = function(value, index) {
        url <- resources_df$url[index]
        if (url != "") {
          tags$a(href = url, target = "_blank", value)
        } else {
          value
        }
      }
    ),
    description = colDef(
      name = "Description",
      minWidth = 300
    ),
    url = colDef(show = FALSE)
  )
)